---
title: "bootstrapping.Rmd"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(patchwork)
```

### Simulate a dataset

```{r}
set.seed(1)

n_samp = 250

sim_df_const =  #constant variance data set
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

Making a plot 

```{r}
sim_df_const %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

Try to repeat this whole process by implementing a procedure which will give better standard error

### Let's try to use the bootstrap for inference

```{r}
# drawing one sample with replacement from the whole dataset
bootstrap_sample = 
  sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>% 
  arrange(x)

lm(y~x, data = bootstrap_sample)
```

Let's write a function...

```{r}
boot_sample = function(df) {
  
  sample_frac(df, size = 1, replace = TRUE)
  
}
```

Now, we'll make a tibble to keep track of everything 

```{r}
boot_strap_df = 
  tibble(
    strap_number = 1:1000, 
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )
```


From here, things are kind of the same as always 

```{r}
boot_strap_results = 
  boot_strap_df %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

boot_strap_results %>% 
  ggplot(aes(x = estimate)) + 
  geom_histogram() + 
  facet_grid(~term, scales = "free")

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy()

boot_strap_results %>% 
  group_by(term) %>% 
  summarize(
    se = sd(estimate)
  )
```

### Use 'modelr' to do the same thing

```{r}
sim_df_nonconst %>% 
  bootstrap(n = 1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  )
```

### Airbnb data 

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()
```

This doesn't give much information ... try this with bootstrapping instead 

```{r}
airbnb_bootstrap_results = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  bootstrap(n = 1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

ggp_star_est = 
  airbnb_bootstrap_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()
  
ggp_scatter = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()

ggp_star_est + ggp_scatter
```

